### 2023-11-22 manuscript.Rmd
Add discussion section on vuong's method

Here, we define the generate function for the tripartite model. The factor loadings specified in step 2 (Design) are called from the condition argument such that they are varied across different iterations of the simulation, and are defined as "a" for syntax readability. For standardization purposes (that is, the total variance of each manifest variable summing up to 1), the loadings of indicators Task5 and Task6 are set to $\frac {a}{\sqrt{(2+2 \cdot cov1)}}$ to account for cross-loadings on multiple factors and are defined as "b" to ease syntax readability (cov1 = covariance between the latent factors pattern separation and pattern completion). The population model is defined by a model string, which specifies three latent factors (ps, pc, gen), measured by the 13 manifest indicators (task1 – task13). The residual variances of the manifest variables are set to $1-a^2$ for standardization purposes. The covariance between the latent factors is set to the respective value from the condition argument. The data are simulated from the model syntax via the simulateData() function from the lavaan package and stored as dat.

@@

### 2.1.4 Step 4: Analyze
In this step, we define the analyze function, which specifies how the data generated in step 3 should be analyzed. For the comparison of non-nested models, we rely on a combination of relative and absolute model fit parameters. We fit each of the competing models to each of the simulated data sets using the sem() function from the lavaan package with a maximum likelihood estimator and extract different measures of model fit using the helper function get_fitmeasures() (see funs.R in the supplementary material on GitHub), namely the Comparative Fit Index [CFI, @bentler_1990], root mean square error of approximation [RMSEA, @steiger_2016] and the Bayesian Information Criterion [BIC, @raftery_1986]. The function returns the fit measures, the simulation model that was used in the respective iteration and information on model convergence. The analyze function for the example on memory composition could thus look like this: 
```{r analyze, echo = TRUE}
```

@@

@@

  The supplementary materials for this article (including the data and R scripts) are publically available at <https://github.com/ebuchberger/Estimating-Power-for-SEM>. The analyses reported in this manuscript were not preregistered.

>>>>

Here, we define the generate function for the tripartite model. The factor loadings specified in step 2 (Design) are called from the condition argument such that they are varied across different iterations of the simulation, and are defined as "a" for syntax readability. For standardization purposes (that is, the total variance of each manifest variable summing up to 1), the loadings of indicators Task5 and Task6 are set to $\frac {a}{\sqrt{(2+2 \cdot cov1)}}$ to account for cross-loadings on multiple factors and are defined as "b" to ease syntax readability (cov1 = covariance between the latent factors pattern separation and pattern completion). Both loading parameters a and b are stored in the list "parameters" such that they can be called via the glue command. The residual variances of the manifest variables are set to $1-a^2$ for standardization purposes. The population model is defined by a model string, which specifies three latent factors (ps, pc, gen) measured by the 13 manifest indicators (task1 – task13), the residual variances as defined above and the covariance between the latent factors as defined in the condition argument. The data are simulated from the model syntax via the simulateData() function from the lavaan package and stored as "dat".

@@

### 2.1.4 Step 4: Analyze
In this step, we define the analyze function, which specifies how the data generated in step 3 should be analyzed. For the comparison of non-nested models, we rely on a combination of relative and absolute model fit parameters (for discussion of an alternative model selection approach, see section 4). We fit each of the competing models to each of the simulated data sets using the sem() function from the lavaan package with a maximum likelihood estimator and extract different measures of model fit using the helper function get_fitmeasures() (see funs.R in the supplementary material on GitHub), namely the Comparative Fit Index [CFI, @bentler_1990], root mean square error of approximation [RMSEA, @steiger_2016] and the Bayesian Information Criterion [BIC, @raftery_1986]. The function returns the fit measures, the simulation model that was used in the respective iteration and information on model convergence. The analyze function for the example on memory composition could thus look like this: 
```{r analyze, echo = TRUE}
```

@@

Further, we have presented an approach that leverages a combination of absolute and relative model fit parameters to adjudicate between competing models. While such parameter-based decisions are well established in the field, they may result in choosing one model over the other, even in cases when differences in model fit parameters are very small, as one can never conclude that two models fit equally well. An alternative approach to this criterion for model selection originates from a theory by @vuong_1989, who suggested likelihood ratio tests for non-nested models. Recent advances that build on this idea have postulated a framework that allows to test hypotheses of model distinguishability and difference in fit [ @levy_2007, @levy_2011], which can be applied to non-nested SEMs and easily implemented via new software packages in R [ @merkle_2016 ]. The resulting recommendations for the comparison of non-nested SEMs posit a stepwise procedure to test whether competing non-nested models are distinguishable in a given population and, if yes, whether one fits the data significantly better than the other. Importantly, this method derives interval estimates for differences in non-nested information criteria [ @merkle_2016 ]. Thus, this approach does not only allow to conclude that one or the other model fits the data better, but also allows for the possibility to conclude that there is insufficient evidence to determine which of two models fits a given dataset better. This stepwise procedure can be implemented as a model selection criterion in a power simulation like the one presented above. To integrate model selection via a likelihood ratio test for non-nested models into the current simulation, one would need to adapt the summarize function accordingly, such that it identifies model 3 as the best fitting model only if a) the competing models are distinguishable on the simulated data set of a given iteration, b) the Likelihood ratio test for non-nested models indicates in a significantly better fit for model 3 compared to models 1 and 2 and c) model 3 reaches the cutoffs for absolute model fit, as defined in the previous simulation. The vuongtest() function from the nonnest2 package [@merkle_2014] can be a helpful tool for integrating these tests into the simulation. While a systematic investigation of the interplay of indicator reliability, separability of latent factors and statistical power for model selection via model fit parameters versus the LRT for non-nested models is beyond the scope of this tutorial, it is worth noting that such an alternative approach may yield better model recovery in certain cases. The conditions under which model selection via the LRT for non-nested models provides better estimates of statistical power are thus an interesting avenue for future research.

@@

  The supplementary materials for this article (including the data and R scripts) are publicly available at <https://github.com/ebuchberger/Estimating-Power-for-SEM>. The analyses reported in this manuscript were not preregistered.
